---
title: "Shiny App Slidy"
author: "MT"
date: "1/24/2021"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = T)
knitr::opts_chunk$set(error = TRUE)
```

## Objectives of this Presentation
- Data used and what is it about
- To explain the purpose of the application
- How to use the application

## Exploring Dataset Used in this Application

```{r, echo = F}
library(HistData)
data(GaltonFamilies)
summary(GaltonFamilies)
```

## Slide with Plot
Using the data set we can observe that there is a trend of children's height when compared to parent's height.
```{r}
library (HistData)
library(ggplot2)
data(GaltonFamilies)
ggplot(GaltonFamilies,aes(x=((father+mother)*2.54)/2, y=childHeight*2.54, color=as.factor(gender))) +
            geom_point(stat="identity") +
            xlab("Average of Parents' Height (cm)") +
            ylab("Children's Height (cm)") +
            theme_minimal() +
            theme(legend.position="none")
```

## Application's Instruction
- Application can be accessed at this [html page](https://merveet.shinyapps.io/shinyapp/)

- Application R code can be accessed at [my github]()

1) Input parent's height on the side panel
2) Select the gender of the child
3) Prediction will be shown on the main panel upon input of height

